### 2017-11-01 submission/manuscript.Rmd
fill in declarations section

Need to fill in.

@@

Need to fill in.

@@

Need to fill in.

@@

Need to fill in.

@@

Need to fill in.

@@

**Table 2: **

```{r table2, echo=FALSE, message=FALSE, warning=FALSE}

@@

@@

>>>>

Ethics approval and informed consent for each of the studies used is mentioned in the respective manuscript used in this meta-analysis.

@@

A detailed and reporducible description of how the data were processed and analyzed for each study can be found at https://github.com/SchlossLab/Sze_CRCMetaAnalysis_Microbiome_2017. Raw sequences can be downloaded from the SRA in most cases and can be found in the respective studies batch file in the GitHub repo or within the original publication. When sequences were not publicly available contacting the corresponding author for raw sequences needs to be undertaken.

@@

MAS is supported by a CIHR fellowship and a University of Michigan PTSP fellowship grant.

@@

All authors helped to design and conceptualize the study. MAS identified and analyzed the data. MAS and PDS interpreted the data. MAS wrote the first draft of the manuscript and both he and PDS reviewed and revised updated versions. All authors approved the final manuscript.

@@

The authors would like to thank all the study participants who were apart of each of the individual studies uitlized. We would also like to thank each of the study authors for making their data available for use. Finally we would like to thank the members of the Schloss lab for valuable feed back and proof reading during the formulation of this manuscript.

@@

@@

**Figure 5: **

**Figure 6: **

@@

**Figure S4: **

**Figure S5: **

**Figure S6: **

**Figure S7: **

**Figure S8: **

### 2017-11-01 submission/manuscript.tex
fill in declarations section

Need to fill in.

@@

\textbf{Table 2: }

@@

@@

>>>>

A detailed and reporducible description of how the data were processed
and analyzed for each study can be found at
\url{https://github.com/SchlossLab/Sze_CRCMetaAnalysis_Microbiome_2017}.
Raw sequences can be downloaded from the SRA in most cases and can be
found in the respective studies batch file in the GitHub repo or within
the original publication. When sequences were not publicly available
contacting the corresponding author for raw sequences needs to be
undertaken.

@@

@@

\textbf{Figure 5: }

\textbf{Figure 6: }

@@

\textbf{Figure S4: }

\textbf{Figure S5: }

\textbf{Figure S6: }

\textbf{Figure S7: }

\textbf{Figure S8: }
